\cvsection{Experience}

\begin{cventries}

  \cventry
    {Data Analyst}
    {Universidad de Concepción}
    {Concepción, Chile}
    {Feb. 2024 - Present}
    {
      \begin{cvitems}
        \item{\textbf{Established a robust pipeline} for consistent generation of new versions of the ETHER sample.}
        \item{\textbf{Consolidated small scripts into a unified infrastructure} and \textbf{conducted analysis on various methods} to estimate black hole masses, considering comparison, systematic differences, and errors.}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Technical Support}
    {Universidad de Concepción}
    {Concepción, Chile}
    {Mar. 2022 - Jan. 2024}
    {
      \begin{cvitems}
        \item{\textbf{Developed a simple algorithm for estimation of black hole masses} using WISE cataloged data.}
        \item{Contributed to various \textbf{publications, presentations, and the creation of observing proposals} for facilities such as ALMA and GMVA, \textbf{securing +100 hours of observing time}.}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Assistantship}
    {Universidad de Concepción}
    {Concepción, Chile}
    {Aug. - Dec. 2023}
    {
      \begin{cvitems}
        \item{Assistant for Extragalactic Astronomy and Radioastronomy classes for 8th-semester astronomy students.}
        \item{Responsible for doing practical classes, making and evaluating homework and exams.}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Research Internship}
    {Harvard University}
    {Cambridge, MA, USA}
    {Mar. - Apr. 2023}
    {
      \begin{cvitems}
        \item{\textbf{Developed and refined WISE2MBH algorithm} at Harvard's Black Hole Initiative.}
        \item{Analyzed black hole emission models within EHT and ngEHT frameworks.}
        \item{\textbf{Developed strong leadership and communication skills} through active team participation, gaining experience in a dynamic research environment.}
      \end{cvitems}
      \vspace{1em}
    }

  \cventry
    {Co-Founder}
    {SciCat}
    {Concepción, Chile}
    {Apr 2020 - Oct. 2022}
    {
      \begin{cvitems}
        \item{Co-founded a non-profit educational support group, \textbf{leading content creation and material development}.}
        \item{Conducted weekly team meetings, managed community engagement on the \cvwebsite{https://www.instagram.com/scicat.cl/}{Instagram} and \cvwebsite{https://www.youtube.com/channel/UC4y3QUrci4jNY9kQ2tiS67A}{YouTube} page, and initiated a website project.}
        \item{\textbf{Secured 5-year financing} for web domain.}
      \end{cvitems}
      \vspace{1em}
    }

\end{cventries}
